Toward an Aspect-oriented Cache Autoloading Framework with Annotation

### 2019-02-17 paper.tex
modified at Feb 16, 2019 - refactor   - section 3.1.4(Auto Loading Strategy) ... done

Figure \ref{autoloading} shows the management of the query autoloading queue. \textit{hashTable}, which providing a method called \textit{putIfAbsent} to avoid duplicate tasks and controlling the number of auto loading tasks, is a storage for auto loading assignments. \textit{taskQueue} is taken from \textit{hashTable} by a unified strategy, like LRU. In distributed scenario, the standardized sequence of tasks help the system reduce the read back of source, because others can fetch data from cache rather than database after first server loaded. Auto loading, however, is a double-edged, the system may become unstable if the amount of auto loading tasks were too much or update frequency were too high. Accordingly, a strict inspection should be applied. We assume that $t_n$(ms) is current time, $t_{fr}$(ms) is the first request time, $t_{lr}$(ms) is last request time,  $t_a$(ms) is the average of fetching time, $c$ is the times of cache usage, $t_{to}$ is a preset parameter determining cache time out. There are three main aspects as follow:

\begin{itemize}
    \item Remove if the targeting cache is not requested for a long time. The time of not be requested is get from $t_{nr} = t_n - t_{lr}$, if $t_{nr} > t_{to}$, the task will be discarded.
    \item Remove if efficiency of fetching data from database is high. This may be confused. The intention of auto loading is pre-load the data that cost a lot of time and resources and be accessed frequently. Hence, the data that obtaining efficiency is high should not occupy the space of auto loading. The standard of determination is $c > 100$ and $t_a < 10$.
    \item Remove if usage rate is low. If the cache, which is requested only once within the preset timeout, were added to auto loading queue, that will go against the purposes of auto loading. Therefore, only removing the task that the targeting cache is not requested for a long time is not enough. The usage rate can be get from $r = \frac{c}{t_u}, t_u = {{t_n - t_{fr}}\over{3600000}}$, the meaning of $r$ is how much the cache is requested per hours. If the task has been running for more than 1 hour and the average loading time is less than 1000 ms and $r$ is less than 60, the task will be removed.
\end{itemize}{}

The last part of auto loading is when to refresh the cache. As a pre-loading schema, the cache should be refreshed before expired. For this reason, setting alarm time is valuable. Experiments prove that the default alarm time should be set $t_e - 120$ if $t_e \geq 600$ or $t_e - 60$ if $t_e < 600$, which $t_e$ is a preset parameter determining cache expired time.

>>>>

Figure \ref{autoloading} shows the management of the query autoloading queue. In the \textit{autoload handler}, there is a hash table, called \textit{autoLoadMap}, which is a storage for auto loading tasks. It provides a \textit{putIfAbsent} method to guarantee each task is different. There is another component, called \textit{taskQueue}, which is taken tasks from \text{autoLoadMap} by a preset strategy, like LRU. ACALFA generates a standardized queue order to ease the database server pressure in the distributed environment, because a server could get the data from another server that just fetched the data from database, instead accesses the database again. Auto loading, however, is double-edged. If a large number of auto loading tasks reside in the memory, this is catastrophic. As the result, they need a lot of cpu and memory resources, even make the system unstable. Thus, a strict inspection measure is required. We assume that $current$(ms) is current time, $first\_request$(ms) is the first request time, $last\_request$(ms) is last request time,  $average$(ms) is the average of fetching time, $cache\_usage$ is the times of cache usage, $time\_out$ is a preset parameter determining cache time out. There are three points ACALFA takes care of.

\textit{A cache is not requested for a long time.} As we mentioned above, auto loading is designed for the hot-spot data. Therefore, the data that is not requested frequently should be removed from auto loading queue, even if it was set auto loading cache in the \textit{@Cache} annotation. This judgement is based on formula \ref{infrequent detections}. If $cost$ is greater than $time\_out$, the respective task will be removed.

\begin{equation}
    cost = current\_time - last\_request
    \label{infrequent detections}
\end{equation}

\textit{The efficiency of fetching data is high and there are a large number of tasks in the queue.} This means querying that data not cost a lot of time or computing resources. If still applies auto loading, it may waste computing resources, which not meets the intention of auto loading. Hence, ACALFA promulgates a policy to prevent that problem happens based on the number of auto loading tasks and the average querying time. If $cache\_usage$ is greater than 100 and $average$ is less than 10, the task will be discarded.

\textit{The usage rate of cache is low.} If the cache was requested only once within every period of $time\_out$ and added into auto loading queue, that will go against the purposes of auto loading. The formula \ref{cache rate} shows how to calculate cache usage rate. If the task has been running for more than 1 hour and the average loading time is less than 1000 ms and $usage\_rate$ is less than 60, the task will be removed.

\begin{equation}
    usage\_rate = \frac{cache\_usage}{current - first\_request}
    \label{cache rate}
\end{equation}

The last part is when to refresh the tasks. In order to keep the cache up to date, we can't refresh it after expired. For this reason, ACALFA sets a field, named alarm time, to avoid it. Experiments prove that alarm time should be set $expired\_time - 120$ if $expired\_time$ greater than 600, otherwise it should be set $expired\_time - 60$. $expired\_time$ is a preset parameter about cache expired time in \textit{@Cache} annotation.
